---
title: "crmSubpathway: identify cancer-related metabolic subpathways"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{crmSubpathway: identify cancer-related metabolic subpathways}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(crmSubpathway)
```

## Introduction
The **crmSubpathway** package is a systematic biological tool to identify cancer-related metabolic subpathways. The main capabilities of this tool are as follows: </br>
1. This function uses the k-clique algorithm to split the metabolic pathways in the KEGG database into metabolic subpathways. </br>
2. A stable metabolic subpathway activity matrix is constructed by GSVA or ssGSEA methods.</br>
3. Cancer-related metabolic subpathways are identified through differential analysis.</br>
4. Visualization

# Mining metabolic subpathways
```{r eval=FALSE, include=FALSE}
library(graph);
library(RBGL);
library(igraph);
library(XML);
file.path<-paste(system.file(package="crmSubpathway"),"/inst/extdata/",sep="")
file.names<-c("hsa00010.xml","hsa00020.xml")
spwlist<-k_clique(file.path,file.names)
```

# Construct metabolic subpathway activity matrix
```{r message=FALSE, warning=FALSE}
library(GSVA)
library(parallel)
# Get the dataset of metabolic subpathways we have processed.
Metspwlist<-get("Metspwlist")
# Get the gene expression profile of the case.
Geneexp<-get("Geneexp")
Spwmatrix<-SubpathwayMatrix(Geneexp,Metspwlist)
head(Spwmatrix)
```

# Identify cancer-related metabolic subpathways
```{r message=FALSE, warning=FALSE}
library(limma)
# Get the metabolic subpathway matrix.
Spwmatrix<-get("Spwmatrix")
spwDF<-CalculateDF(Spwmatrix,colnames(Spwmatrix),"cancer","control")
```

# Visualize
```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
library(igraph)
plotNetGraph(spwid="00010_1")
```
```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
library(pheatmap)
DFspw<-get("DFspw")
plotspwheatmap(DFspw,cluster_rows = TRUE,show.colnames=FALSE)
```
